% Add Acknowladgement to TOC
\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

I would like to express my sincere gratitude to my thesis supervisor, Prof. Yoichiro Kato of the Graduate School of Agricultural and Life Sciences, for his invaluable advice, support, guidance, and encouragement throughout my doctoral research journey. He has constantly challenged and guided me to push the boundaries of my research and finally bring me to the point of accomplishing my degree.

I would also like to extend my thanks to the members of my thesis committee, [todo] committee memeber's names, for their valuable feedback and insights. Their contributions have significantly improved the quality and relevance of my research.

Furthermore, I would like to thank Dr. Wei Guo. He not only served almost like a role of an advisor who greatly helped with my doctoral studies but also as a close friend who gave me many valuable suggestions for both academic and daily life in Japan. Also thank Dr. Yuji Yamasaki from The University of Tokyo, Dr. Yuya Fukano from Chiba University, Dr. Wenli Zhang from Beijing University of Technology, Dr. Yun Shi and Dr. Yulin Duan from Chinese Academy of Agricultural, and Dr. Feng Wang from Chinese Academy of Forestry, for providing me with advanced resources and excellent academic support.

I would also like to thank Naomi Morinaga, Kozue Wada, Alexander Feldman, Kunihiro Kodama, Masanori Ishii, and all the technical support staffs of \gls{isas} for providing me with a conducive research environment and excellent support for fieldwork and document-related work. It enabled me to freely explore and develop my research interests.

I am also extremely grateful to my labmates. Tang Li is a good friend who helped me a lot with deep learning and life in Japan, and Nishida Erika contributed greatly to the broccoli fieldwork. I also thank my tutors, Thum Chun Hau and Jaesuk IM, for their kind help, and all my other friends for being the pillars of my life.

I would also like to express my gratitude to my family for their constant support, encouragement, and love, especially my girlfriend who has never appeared in my actual life and has allowed me to fully focus on my academic work.

Thank you all for being an integral part of my doctor journey and for helping me achieve this milestone.